### 2016-11-22 local-capability-machine.tex
Comment

  \item Create local enter capability for restoration

@@

  \item [Create local enter capability for restoration]
    Make a new version of the stack pointer that points to the beginning of the restoration code. Restrict it to a local-enter capability and put it in $r_0$.

>>>>

  \item Create protected return pointer

@@

  \item [Create protected return pointer]
    Make a new version of the stack pointer that points to the beginning of the restoration code. Restrict it to a local enter-capability and put it in $r_0$. \lau{Do we want to use ``protected return pointer'' to mean a local enter capability?}
